Are rankings of financial analysts useful to investors?

### 2015-04-01 doc/paper/paper-knitr-APS.Rnw
switched to 'all' selected stocks.

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
\pagestyle{empty}
%\pagestyle{fancy}

@@

sel.s <- 'same'

@@

\title{Are rankings of financial analysts useful to investors?}
%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
% 
% \affil[1]{FEP \& CEF.UP, University of Porto}
% \affil[2]{INESC TEC}
% \affil[4]{FEUP, University of Porto}

\maketitle
% You need this here, or else the first page won't have a header.
%\thispagestyle{fancy}

@@

Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks. Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised. After one year we assume that TP recommendation expires.

Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view,na.rm=T)]}). This is done due to occurrence of the extreme values. Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases. In some cases the stock-splits and the dividends were not properly adjusted.}. After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. Finally, we consider stocks that have both EPS and TP forecasts in a given quarter. The total number of stocks in our sample, thus, is \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} stocks.

>>>>

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
%\pagestyle{empty}
\pagestyle{fancy}

@@

sel.s <- 'all'

@@

\title{Are rankings of financial analysts useful to investors?}
 \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
 \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
 \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}

\affil[1]{FEP \& CEF.UP, University of Porto}
\affil[2]{INESC TEC}
\affil[4]{FEUP, University of Porto}

\maketitle
% You need this here, or else the first page won't have a header.
\thispagestyle{fancy}

@@

Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} S\&P500 stocks. Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised. After one year we assume that TP recommendation expires.

Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view,na.rm=T)]}). This is done due to occurrence of the extreme values. Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases. In some cases the stock-splits and the dividends were not properly adjusted.}. We also require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). After all necessary data requirements, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(pt.rank.views[,.N],big.mark=' ')}.

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. We apply the same data requirements as in case of TP dataset (minimum 3 brokers per stock and 12 quarters of coverage). Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.rank.views[,.N,by=Stock][,.N]} stocks

Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.

### 2015-04-01 doc/paper/paper-knitr-APS.tex
switched to 'all' selected stocks.

The initial file of quarterly EPS forecast consists of  560 brokers covering 3517 stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our final sample of EPS forecasts consist of  155 brokers covering 402 stocks. The total number of observation is 79 539.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.615\%, and 18.615\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%). Panel C shows the EPS based weighted expected returns averages (14.696\%, 14.895\%, and 12.857\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.288\%, 0.565\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.292 against NA, 0.036, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.681\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.323\% and 0.738\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & - & - & - & - & - & - \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.876 & 15.191 & 13.369 & 13.595 & 0.096 & 0.096 \\ 
  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
  \default{} & 12.461 & 12.718 & 10.588 & 10.789 & 0.088 & 0.089 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.696 & 14.774 & 13.233 & 13.269 & 0.101 & 0.102 \\ 
  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
  \default{} & 12.857 & 12.928 & 11.410 & 11.440 & 0.089 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 & - & - &   73 &   69 &   44 &   44 \\ 
  2000 & - & - &  253 &  232 &  191 &  191 \\ 
  2001 & - & - &  302 &  273 &  244 &  244 \\ 
  2002 & - & - &  354 &  317 &  290 &  290 \\ 
  2003 & - & - &  369 &  330 &  299 &  299 \\ 
  2004 & - & - &  375 &  331 &  318 &  318 \\ 
  2005 & - & - &  395 &  347 &  337 &  337 \\ 
  2006 & - & - &  403 &  351 &  337 &  337 \\ 
  2007 & - & - &  418 &  359 &  351 &  351 \\ 
  2008 & - & - &  414 &  354 &  339 &  339 \\ 
  2009 & - & - &  346 &  306 &  306 &  306 \\ 
   \midrule 
Total & - & - &  442 &  378 &  375 &  375 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   44 &   44 \\ 
  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
  2002 &  362 &  323 &  362 &  323 &  288 &  288 \\ 
  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  376 &  376 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
  2002 &  362 &  323 &  362 &  323 &  304 &  304 \\ 
  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  377 &  377 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
  &all&same&all&same&all&same&all&same&all&same \\

 \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
  \textit{TP} & 4.288 & 4.512 & 14.695 & 14.792 & 0.292 & 0.305 &  284 &  251 & 0.344 & 0.326 \\ 
  \textit{EPS} & 0.565 & 0.718 & 15.541 & 15.509 & 0.036 & 0.046 &  205 &  205 & 0.495 & 0.493 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.126 & 0.449 & 15.947 & 15.993 & 0.008 & 0.028 &  284 &  252 & 0.256 & 0.250 \\ 
  \textit{TP} & 0.281 & 0.622 & 15.661 & 15.682 & 0.018 & 0.040 &  284 &  252 & 0.264 & 0.256 \\ 
  \textit{EPS} & -0.318 & -0.361 & 16.094 & 16.100 & -0.020 & -0.022 &  206 &  206 & 0.409 & 0.408 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.323 & 0.702 & 15.771 & 15.820 & 0.020 & 0.044 &  284 &  252 & 0.228 & 0.223 \\ 
  \textit{TP} & 0.681 & 1.043 & 15.553 & 15.476 & 0.044 & 0.067 &  284 &  252 & 0.256 & 0.248 \\ 
  \textit{EPS} & 0.738 & 0.711 & 15.446 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.255 \\

>>>>

The initial file of quarterly EPS forecast consists of  560 brokers covering 3517 stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our sample of EPS forecasts consist of  155 brokers covering 402 stocks. Finally, we consider stocks that have both EPS and TP forecasts in a given quarter. The total number of stocks in our sample, thus, is 442 stocks.

%The total number of observation is prettyNum(complete.dt[,.N],big.mar=' ').

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, 18.615\%, and 18.615\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%). Panel C shows the EPS based weighted expected returns averages (14.696\%, 14.895\%, and 12.857\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, 4.288\% and 0.565\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.292 against 0.036 and \ensuremath{-0.182}, respectively, for the \textit{EPS} and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\% and  0.126\% respectively. The active strategy based on EPS forecasts, demonstrated negative annualized cumulative return of \ensuremath{-0.318}\%.

%Moreover, comparing the smart estimate and the consensus based strategy, observe that the former outperforms the latter confirming that rankings can identify the best analsyts

The \textit{TP} strategy also dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} further confirms the outperformance of the \textit{TP} smart strategy: under the \default{} information set it yields the highest annualized cumulative return  of 0.681\% comparing to the \textit{CONS} and the \textit{EPS} strategies (0.323\% and 0.738\% respectively). The panel C of table \ref{tab:substrategy} shows that \textit{TP} strategy is also dominant in every sub-periods.

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%)&Median (in \%)&Std.dev\\
%&all&same&all&same&all&same\\
\midrule
  \multicolumn{4}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & - & - & - \\ 
  \naive{} & 18.615 & 16.866 & 0.120 \\ 
  \default{} & 18.615 & 16.866 & 0.120 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
  \multicolumn{4}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.876 & 13.369 & 0.096 \\ 
  \naive{} & 15.738 & 14.304 & 0.098 \\ 
  \default{} & 12.461 & 10.588 & 0.088 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.696 & 13.233 & 0.101 \\ 
  \naive{} & 14.895 & 13.393 & 0.103 \\ 
  \default{} & 12.857 & 11.410 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
%&all&same&all&same&all&same\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 & - &   73 &   44 \\ 
  2000 & - &  253 &  191 \\ 
  2001 & - &  302 &  244 \\ 
  2002 & - &  354 &  290 \\ 
  2003 & - &  369 &  299 \\ 
  2004 & - &  375 &  318 \\ 
  2005 & - &  395 &  337 \\ 
  2006 & - &  403 &  337 \\ 
  2007 & - &  418 &  351 \\ 
  2008 & - &  414 &  339 \\ 
  2009 & - &  346 &  306 \\ 
   \midrule 
Total & - &  442 &  375 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   73 &   73 &   44 \\ 
  2000 &  257 &  257 &  185 \\ 
  2001 &  310 &  310 &  247 \\ 
  2002 &  362 &  362 &  288 \\ 
  2003 &  374 &  374 &  307 \\ 
  2004 &  385 &  385 &  318 \\ 
  2005 &  401 &  401 &  337 \\ 
  2006 &  415 &  415 &  343 \\ 
  2007 &  421 &  421 &  352 \\ 
  2008 &  422 &  422 &  349 \\ 
  2009 &  405 &  405 &  321 \\ 
   \midrule 
Total &  442 &  442 &  376 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   73 &   73 &   54 \\ 
  2000 &  257 &  257 &  204 \\ 
  2001 &  310 &  310 &  261 \\ 
  2002 &  362 &  362 &  304 \\ 
  2003 &  374 &  374 &  317 \\ 
  2004 &  385 &  385 &  332 \\ 
  2005 &  401 &  401 &  344 \\ 
  2006 &  415 &  415 &  353 \\ 
  2007 &  421 &  421 &  358 \\ 
  2008 &  422 &  422 &  359 \\ 
  2009 &  405 &  405 &  350 \\ 
   \midrule 
Total &  442 &  442 &  377 \\

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\

 \textit{CONS} & - & - & - & - & - \\ 
  \textit{TP} & 4.288 & 14.695 & 0.292 &  284 & 0.344 \\ 
  \textit{EPS} & 0.565 & 15.541 & 0.036 &  205 & 0.495 \\ 
   \midrule

\begin{tabularx}{\linewidth}{r*{6}{Y}}
  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
   \midrule

\begin{tabularx}{\linewidth}{r*{6}{Y}}
  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.323 & 15.771 & 0.020 &  284 & 0.228 \\ 
  \textit{TP} & 0.681 & 15.553 & 0.044 &  284 & 0.256 \\ 
  \textit{EPS} & 0.738 & 15.446 & 0.048 &  245 & 0.256 \\
